### 2024-08-14 getting-started.qmd
20240812 - typo
20240814 - placeholder for piping
20240814 - piping

1. Set up a free account on [GitHub.com](https://github.com).
1. Download GitHub Desktop: <https://desktop.github.com>
1. Make sure you are logged into your GitHub account on [GitHub.com](https://github.com).
1. Go to the following GitHub repository: <https://github.com/isaactpetersen/QuartoBlogFantasyFootball> and complete the following steps:
    1. Click "Use this Template" (in the top right of the screen) > "Create a new repository"
    1. Make sure the checkbox is selected for the following option: "Include all branches"
    1. Make sure your Owner account is selected
    1. Specify the repository name to whatever you want, such as `FantasyFootballBlog`
    1. Type a brief description, such as `Files for my fantasy football blog`
    1. Keep the repository public (this is necessary for generating your blog)
    1. Select "Create repository"
1. After creating the new repository, make sure you are on the page of of your new repository and complete the following steps:
    1. Click "Settings" (in the topof the screen)
    1. Click "Actions" (in the left sidebar) > "General"
    1. Make sure the following are selected:
        - "Read and write permissions" (under "Workflow permissions")
        - "Allow GitHub Actions to create and approve pull requests"
        - then click "Save"
    1. Click "Pages" (in the left sidebar)
    1. Make sure the following are selected:
        - "Deploy from a branch" (under "Source")
        - "gh-pages/(root)" (under "Branch")
        - then click "Save"
1. Clone the repository to your local computer by clicking "Code" > "Open with GitHub Desktop", select the folder where you want the repository to be saved on your local computer, and click "Clone"
:::

@@

>>>>

1. Set up a free account on [GitHub.com](https://github.com).
1. Download GitHub Desktop: <https://desktop.github.com>
1. Make sure you are logged into your GitHub account on [GitHub.com](https://github.com).
1. Go to the following GitHub repository: <https://github.com/isaactpetersen/QuartoBlogFantasyFootball> and complete the following steps:
    1. Click "Use this Template" (in the top right of the screen) > "Create a new repository"
    1. Make sure the checkbox is selected for the following option: "Include all branches"
    1. Make sure your Owner account is selected
    1. Specify the repository name to whatever you want, such as `FantasyFootballBlog`
    1. Type a brief description, such as `Files for my fantasy football blog`
    1. Keep the repository public (this is necessary for generating your blog)
    1. Select "Create repository"
1. After creating the new repository, make sure you are on the page of of your new repository and complete the following steps:
    1. Click "Settings" (in the top of the screen)
    1. Click "Actions" (in the left sidebar) > "General"
    1. Make sure the following are selected:
        - "Read and write permissions" (under "Workflow permissions")
        - "Allow GitHub Actions to create and approve pull requests"
        - then click "Save"
    1. Click "Pages" (in the left sidebar)
    1. Make sure the following are selected:
        - "Deploy from a branch" (under "Source")
        - "gh-pages/(root)" (under "Branch")
        - then click "Save"
1. Clone the repository to your local computer by clicking "Code" > "Open with GitHub Desktop", select the folder where you want the repository to be saved on your local computer, and click "Clone"
:::

@@

## Piping {#sec-piping}

In base `R`, if you want to perform multiple operations, it is common to either a) nest the operations, or b) save the object at each step.

Below is an example of nested operations:

```{r}
length(names(nfl_players))
```

Below is an example of saving the intermediate object at each step:

```{r}
variableNames <- names(nfl_players)
variableNames

lengthOfVariableNames <- length(variableNames)
lengthOfVariableNames
```

Code for performing nested operations can be challenging to read.
Saving the intermediate object can be a waste of time to do if you are not interested in the intermediate object, and can take up unnecessary memory and computational resources.
An alternative approach is to use piping.
Piping allows taking the result from one computation and sending it to the next computation, thus allowing a chain of computations without saving the intermediate object at each step.

In base `R`, you can perform piping with the `|>` expression.
In `tidyverse` you can perform piping with the `%>%` expression.

#### Base `R` {#sec-pipingBaseR}

```{r}
nfl_players |>
  names() |>
  length()
```

#### Tidyverse {#sec-pipingTidyverse}

```{r}
nfl_players %>%
  names() %>%
  length()
```
